### 2013-04-22 0_frontmatter/abstract.tex
added 201304_Apr22

Put your abstract or summary in 0\_frontmatter/abstract.tex.

>>>>

In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.

With (POL)SAR data becomes cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. %it is of great important to understand the data.
The SAR data, however is stochastic by nature, due to the interference phenomena of EM waves. %, SAR measurements are stochastic by nature.
Under this condition, it is very important to understand the statistical models for SAR data.
It is these models that form the foundation for different SAR data processing techniques,
  for example speckle filtering, target detection, image segmentation, and other clustering, classification techniques.
Central to these machine learning or signal processing algorithms is the need for consistent discrimination measures which are derived from the statistical models.

While the statistical models for homogeneous SAR areas have long been developed and widely used,
  in extending the model toward heterogeneous images, the impact of the heteroskedastic property in these models has virtually been ignored.
Specifically the concept of distance as a measure of dis-similarity is seriously flawed,
  as it is widely known that ratio offers a better discrimination measure for SAR \cite{Rignot_1993_TGRS_896}.
This thesis starts off by proposing the logarithmic transformation which is shown converting the SAR data into an homoskedastic model.
Within this log-transformed domain, a few consistent measures of distance is proposed. 
In a sense the distance concept is re-emerged, as the log-transformation converts the widely used ratio into standard subtractive distance.

In extending our statistical understanding of SAR data towards multi-dimensional POLSAR data, an important issue needs to be addressed.
The trouble that the high dimensional data bring about is that there exists not one, as the intensity in the one-channel SAR, but many observables quantities in multi-channel POLSAR.
While different statistical models have been developed for different POLSAR observables,
  for a statistical model to be useful, scalar discrimination measures need to be derived from.
Thus on the one hand, practical application for POLSAR data processing requires the measure to be scalar, consistent and preferably homoskedastic. % on the one hand.
On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.

In this thesis, the determinant of the POLSAR covariance matrix is proposed as an observable quantity to study.
The representative power of this observable is demonstrated when the multi-dimensional POLSAR data is collapsed into the traditional one-dimensional SAR scenario, the determinant then is transformed into the standard SAR intensity.
Statistical models for this heteroskedastic POLSAR determinant and homoskedastic log-determinant are then derived.
And since POLSAR can be viewed as a multi-dimensional extension of SAR, the thesis describes how the standard statistical models for SAR can be put within the natural coverage of this generic models for POLSAR.
%Subsequently logarithmic transformation is investigated for this generalized SAR model,
%  which lead to the proposal for several linear and additive measures of distance for POLSAR.

%There are a few benefits of using the homoskedastic measures of distance for POLSAR.
In short, to address the dual-problem described above,
  this thesis proposes several scalar, additive and homoskedastic measures of distance for the multi-dimensional, multiplicative and heteroskedastic POLSAR data. 
%The proposed statistical models and the homoskedastic measures of distance for POLSAR bring about a couple of benefits. 
There are a couple of benefits in using these homoskedastic measures of distance for (POL)SAR.
First, compared to the multiplicative dis-similarity measure of ratio, these additive measures of distance fit more naturally with the linear nature of digital imagery.
Second, within the homoskedastic log-transformed domain, where the distance concept as well as the Gauss-Markov theorem is again applicable,
  the use of Mean Squared Error (MSE) as universal objective function deserves to be reviewed. % as a reliable objective function / criteria for (POL)SAR estimators.
%This may open up a number of different research directions for future studies of (POL)SAR.
As example applications of how these statistical models and distance measures,
  a novel clustering algorithm, a new speckle filter and various procedures in using MSE to evaluate speckle filters are also presented as part of the thesis.

### 2013-04-22 1_introduction/introduction.tex
added 201304_Apr22

% the code below specifies where the figures are stored
%\ifpdf
%    \graphicspath{{1_introduction/figures/PNG/}{1_introduction/figures/PDF/}{1_introduction/figures/}}
%\else
%    \graphicspath{{1_introduction/figures/EPS/}{1_introduction/figures/}}
%\fi

% ----------------------------------------------------------------------
%: ----------------------- introduction content ----------------------- 
% ----------------------------------------------------------------------

@@

%: ----------------------- HELP: latex document organisation
% the commands below help you to subdivide and organise your thesis
%    \chapter{}       = level 1, top level
%    \section{}       = level 2
%    \subsection{}    = level 3
%    \subsubsection{} = level 4
% note that everything after the percentage sign is hidden from output

	\section{Background Context and the Motivation to Study}

%Advantages of SAR in remote sensing paragraph (page 3)
Synthetic Aperture Radar can soon become the preferred choice for
  continous and autonomous large-scale remote surveillance solutions.
Compared to optical remote sensors, which is passive,
  active SAR sensors provides weather independent and night-inclusive operational capabilities.
Compared to other radar based active sensors, for example Real Aperture Radar (RAR),
  SAR provides a much better resolution, and larger coverage solution.
The once-limiting drawback of SAR is the high-demanding signal processing procedures,
  which is needed to process SAR images, has become obsolete,
  due to recent and quick advances in computational power  \citep{Cumming_2005_Artech}.

EM wave polarization and polarimetric SAR paragraph (page 3)

A paragraph about partial polsar and the extension from (page 3)

@@

For SAR data (page 4)

For partial POLSAR data (new)

For full polsar data (new)

The purpose of this section is to illustrate the importance of a computational framework needed in the interpretation and processing targets' stochastic polarimetry signatures. 
%This section start by describing the recent focus of space technology in earth observational remote sensing.
As reviewed in the second chapter, Synthetic Aperture Radar, i.e. SAR, offers a higher resolution, large coverage, weather-independent and night-capable imaging solution.
Recent advances in computational power has made the once-limiting high-demanding signal-processing procedures, which are needed to process SAR images, obsolete \cite{Cumming_2005_Artech}.
Thus we believe, SAR will soon come to be the preferred choice for continuous and autonomous large-scale remote surveillance solutions.

The extensions from single-channel SAR to multi-channel polarimetry can be considered as analogous to the advancement towards colour TV from the black-and-white days.
While the future is promising, both SAR and POLSAR suffer from speckle phenomena, which hampers the human capabilities to understand SAR images.
Speckle, which arises due to the random interference of many de-phased but coherent back-scattered waves, is inherent in all channels.
The effects of speckle is illustrated in Figure \ref{fig:sar_speckle_wrt_optical}.

%%TODO: SWITCH IMAGES: 24 lines
%\begin{figure}[h!]
%\centering
%	\subfloat[Optical Colour Image]{
%		 \epsfxsize=1.75in
%		 \epsfysize=1.75in
%		 \epsffile{images/20100502_mris_clipped.eps} 	
%		 \label{Original}
%	} 
%	\hfill
%	\subfloat[Optical Gray level image]{
%		 \epsfxsize=1.75in
%		 \epsfysize=1.75in
%		\epsffile{images/20100502_mris_clipped_gray.eps}
%		 \label{}
%	}
%	\hfill
%	\subfloat[Speckled SAR image]{
%		 \epsfxsize=1.75in
%		 \epsfysize=1.75in
%		 \epsffile{images/20100502_sar.eps} 	
%		 \label{Original}
%	} 
%\caption{Speckle phenomena in SAR data}
%\label{fig:sar_speckle_wrt_optical}
%\end{figure}

@@

For single-channel SAR images, our initial observations and experiences indicate that the community has been oblivious to many of the negative effects of statistical heteroskedasticity manifested in the original intensity and amplitude data.
In Chapter 4, it is shown that logarithmic transformation can convert SAR's multiplicative stochastic process into a better-understood additive noise model.
Thus, the additive-noise domain indicates homoskedasticity as well as offers a consistent sense of distance and variance.
As the additive noise PDF in log-domain has been worked out, we hypothesize that the true back-scattering coefficient PDF, also in log-domain, can be estimated through regularized deconvolution algorithms.
If an algorithm could be designed to estimate such PDF, we believe this would present an improvement for a whole class of speckle filters, namely the Maximum-A-Priori (MAP) class, which up to now, still assumes the true PDF will follow certain known fixed distributions.
%It is hoped that with the true PDF now being estimatable from the data itself, a better speckle filtering algorithm, in log-transformed domain, can be developed.

For multi-channel SAR data, as reviewed in Chapter 2, speckle filtering for the off-diagonal element $S_hS_v^*$ of the covariance matrix is still an open question.
Our observation has been that these elements are also available in dual-polarization SAR data, they specifically are part of Stokes parameters.
As mentioned earlier, Stokes parameters have been largely ignored in polarimetric literature, until recently asserted again by Raney in 2006 \cite{Raney_2006_IGARSS}.
Mathematically, Stokes parameters can be written as:
\begin{equation}
S = 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		2 \Re{(S_hS_v^*)} \\
		2 \Im{(S_hS_v^*)}
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		S_+S_+ - S_-S_- \\
		S_lS_l - S_rS_r
	\end{array}
\right)
\end{equation}
We have evidence, and hypothesize that $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ will have the same physical and statistical properties as the normal $S_hS_h$, $S_vS_v$.
If our hypothesis can be proven rigorously, it may then be possible to build and validate a statistical model for all elements in the covariance matrix of Polarimetric SAR data, namely $S_hS_h$, $S_vS_v$, $\Re{( S_hS_v^*)}$, $\Im{( S_hS_v^* )}$.
Also, speckle filtering on off-diagonal elements can be carried out using techniques, that were originally developed for single-channel SAR data, and up to now is only applicable to the diagonal elements of the covariance matrix.

For the topic of target (ship) detection and classification, we notice that the use of partial polarimetry will provide extra polarimetry data without incurring loss in spatial resolution.
We proceed to hypothesize that: partial polarimetry will lead to improved target (ship) detection and classification accuracy in comparision to traditional SAR data.
Experiments can be carried out by capturing polarimetric SAR remote sensing imagery and ground truth data which is provided via the ships' locational identification data.
Automatic Identification System (AIS), which normally supplements marine radars, is a standard ship tracking system for identifying and locating floating vessels.
Empirical evidence can be obtained by applying traditional ship detection and classification on traditional and polarimetric data concurrently, and the results are to be compared.
%Besides the empirical evidences that we plan to obtain, we hope that once our work on statistical modelling of partial polarimetry has taken shape, the hypothesis can be rigorously proven by statistical mathematics.

@@

Copy the objectives (page 6)

copy the benefits (page 6)

\subsection{Objectives and Contributions}

@@

\subsection{The Research Questions}

@@

\subsubsection{Theory Development and Research Strategy}
For single channel SAR data, we propose the use of a log transform to evaluate speckle filter's performance. 
We have proved that homoskedasticity property is indeed manifested in the log-domain.
The traditional performance index in comparing speckle filters, i.e. the Equivalent Number of Looks (ENL), has also been shown to be related and calculable from the standard Mean Squared Error (MSE) inside the log-domain.
We are working to prove that, with the homoskedastic property asserted, the universal Mean Squared Error can be a good performance indicator, even on heterogeneous spatial variations.

Furthermore, as the point spread function (PSF) is available in the log-transformed domain, it appears that, for the first time, the histogram of the underlying back-scattering coefficient may become estimate-able. 
In figure 
	\ref{fig:noise_pdf_as_psf:conv_inputs}, 
the underlying single channel gray image histogram is presented along with the noise PDF, in the log-transformed domain. 
As the noise is additive, it is expected that the noise PDF will act as a point spread function.
This makes the observable speckled image histogram mathematically equivalent to the convolution of the original image's histogram and the noise PDF.
This fact is evidenced in figure 
	\ref{fig:noise_pdf_as_psf:conv_output_observable}, 
where except for the un-calibrated shifting, the shapes of theoretical convolution and observed histogram are reasonably similar.
We hypothesize that: given the observable SAR data and its histogram, it should be possible to estimate the original underlying signal's histogram through some regularized deconvolution methods.
We intended to start by applying the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical} for such estimations.

\begin{figure}[h!]
\centering
	\subfloat[Original image's histogram and PSF]{
		 \epsfxsize=3in
		 \epsfysize=3in
 		 \epsffile{images/log_PSF_NTU_gray_histogram.eps}
		 \label{fig:noise_pdf_as_psf:conv_inputs}
	} 
	\hfill
	\subfloat[Convoluted and speckled image histogram]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/log_convoluted_NTU_speckled_histogram.eps} 	
		 \label{fig:noise_pdf_as_psf:conv_output_observable}
	}
\caption{Observable convolution of PSF}
\label{fig:noise_pdf_as_psf}
\end{figure}

For multi-channel SAR data, we focus on partial polarimetric SAR satellite data.
Attempts have been made to model the data, especially the off-diagonal covariance matrix elements, i.e. $S_hS_v^*$.
However, the models are overly complicated which made proposed PolSAR speckle suppression algorithms became overly complex (see polarimetric data modelling section in Chapter 2).
We preferred an alternative approach.
We propose to transform the polarization basis of dual-polarized SAR data to help estimate this element.

We first pick up a recent revelation by Raney, 2006 \cite{Raney_2006_IGARSS}, that the back scattering waves' polarization captured in dual-pol data can be completely described using Stokes parameters.
%From the usually given pairs of $S_h$ and $S_v$, Raney has shown that Stokes parameters can be computed.
Furthermore, Stokes parameters can be measured in multiple polarization basis, which can also be synthesized from the given data (see polarization basis transform section in Chapter 2).
%Both transformations, i.e. from $\{h,v\}$ to circular basis $\{l,r\}$ and from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ modes, are special cases of the transformation formula.
That is:
	the measured signal at $\pi/4$ linear polarizer as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.

The Stokes vectors, when aligned at these transformed projections are given by the following well-known equation:
\begin{equation}
S_t = \left(
\begin{array}{c}
 |\xi_h|^2 + |\xi_v|^2 \\
 |\xi_h|^2 - |\xi_v|^2 \\
 2 \Re( \xi_h \xi_v^* ) \\
 2 \Im( \xi_h \xi_v^* ) 
\end{array}
\right)
= \left(
\begin{array}{c}
 |\xi_+|^2 + |\xi_-|^2 \\
 -2 \Re( \xi_+^* \xi_- ) \\
 |\xi_+|^2 - |\xi_-|^2 \\
 2 \Im( \xi_+^* \xi_- ) 
\end{array}
\right)
= \left(
\begin{array}{c}
 |\xi_l|^2 + |\xi_r|^2 \\
 2 \Re( \xi_l^* \xi_r ) \\
 -2 \Im( \xi_l^* \xi_r ) \\ 
 |\xi_l|^2 - |\xi_r|^2 
\end{array}
\right)  
\end{equation}

Evidently, the real and imaginary parts of $S_hS_v^*$ is closely related to Stokes Parameters.
Specifically they may be considered as the subtraction of two random SAR intensity variables, e.g., $|S_l|^2 - |S_r|^2$. 
%Since ShSh is exponential this can be calculated through convolutions, if each channels are independent. 
%Laplace distribution is the difference between two identical exponential distributions. 
For the same traditional reasoning of $|S_h|^2$ and $|S_v|^2$, we hypothesize that all the four intensities calculated from the transformation of polarization basis, i.e., $|S_+|^2$, $|S_-|^2$, $|S_l|^2$, $|S_r|^2$, follow negative exponential distributions. 
The hypothesis is supported by our preliminary experiment results, where we synthesize the basis transformed intensity from real-measured polarimetric data.
It then follows that $S_hS_v^*$ can be despeckled by independently de-speckling the four synthesized intensities.
Read chapter 4 for our work in progress in single-channel SAR speckle filtering.
We hope to go further speculating that: the speckle-filtering methodologies in dual-polarization SAR data is extensible to full polarimetric SAR data.

@@

To demonstrate the use of partial polarimetry for target detection and classification tasks, we could proceed with either approach.
The first approach being: first full polarimetric information is to be reconstructed from partial polarimetry data.
Then standard full polarimetric target detection and classification techniques can be applied on synthesized data.
Read Chapter 3 for our published work in extending the reconstruct-ability of full polarimetric information from partial polarimetry data to urban and man-made areas.
The second approach would be to invent a totally new target detection algorithm making use of the fact that partial polarimetric data also contains certain basic information about the target's polarimetric signature (see partial polarimetry section in Chapter 2).

>>>>

Synthetic Aperture Radar can soon become the preferred choice for
  continous and autonomous large-scale remote surveillance solutions.
Compared to optical remote sensors, which is passive,
  active SAR sensors provides weather independent and night-inclusive operational capabilities.
Compared to other radar based active sensors, for example Real Aperture Radar (RAR),
  SAR provides a much better resolution, and larger coverage solution.
The once-limiting drawback of SAR is the high-demanding signal processing procedures,
  which is needed to process SAR images, has become obsolete,
  due to recent and quick advances in computational power  \citep{Cumming_2005_Artech}.

As reviewed in the second chapter, Synthetic Aperture Radar, i.e. SAR, offers a higher resolution, large coverage, weather-independent and night-capable imaging solution.
Recent advances in computational power has made the once-limiting high-demanding signal-processing procedures, which are needed to process SAR images, obsolete \cite{Cumming_2005_Artech}.
Thus we believe, SAR will soon come to be the preferred choice for continuous and autonomous large-scale remote surveillance solutions.

The extensions from single-channel SAR to multi-channel polarimetry can be considered as analogous to the advancement towards colour TV from the black-and-white days.
While the future is promising, both SAR and POLSAR suffer from speckle phenomena, which hampers the human capabilities to understand SAR images.
Speckle, which arises due to the random interference of many de-phased but coherent back-scattered waves, is inherent in all channels.
%The effects of speckle is illustrated in Figure \ref{fig:sar_speckle_wrt_optical}.

\section{The Research Question and the Motivation to Study}

@@

@@

@@

For single-channel SAR images, our initial observations and experiences indicate that the community has been oblivious to many of the negative effects of statistical heteroskedasticity manifested in the original intensity and amplitude data.
In Chapter 4, it is shown that logarithmic transformation can convert SAR's multiplicative stochastic process into a better-understood additive noise model.
Thus, the additive-noise domain indicates homoskedasticity as well as offers a consistent sense of distance and variance.

%\subsection{The Research Questions}

%For the topic of target (ship) detection and classification, we notice that the use of partial polarimetry will provide extra polarimetry data without incurring loss in spatial resolution.
%We proceed to hypothesize that: partial polarimetry will lead to improved target (ship) detection and classification accuracy in comparision to traditional SAR data.
%Experiments can be carried out by capturing polarimetric SAR remote sensing imagery and ground truth data which is provided via the ships' locational identification data.
%Automatic Identification System (AIS), which normally supplements marine radars, is a standard ship tracking system for identifying and locating floating vessels.
%Empirical evidence can be obtained by applying traditional ship detection and classification on traditional and polarimetric data concurrently, and the results are to be compared.
%Besides the empirical evidences that we plan to obtain, we hope that once our work on statistical modelling of partial polarimetry has taken shape, the hypothesis can be rigorously proven by statistical mathematics.

@@

\subsection{The Research Objectives}

@@

@@

@@

%To demonstrate the use of partial polarimetry for target detection and classification tasks, we could proceed with either approach.
%The first approach being: first full polarimetric information is to be reconstructed from partial polarimetry data.
%Then standard full polarimetric target detection and classification techniques can be applied on synthesized data.
%Read Chapter 3 for our published work in extending the reconstruct-ability of full polarimetric information from partial polarimetry data to urban and man-made areas.
%The second approach would be to invent a totally new target detection algorithm making use of the fact that partial polarimetric data also contains certain basic information about the target's polarimetric signature (see partial polarimetry section in Chapter 2).
